Panthera: A Study of Caching in Distributed Computing

### 2014-03-01 paper/paper.tex
paper font change

\documentclass{article}

@@

\section{Introduction}
Distributed computing systems are currently employed across academia and industry. Applications vary from market research for department stores to bioinformatics. In particular, the Hadoop distributed system \cite{hadoop} has seen tremendous growth. Hadoop is an open source version of the revolutionary MapReduce system developed at Google. With it, developers can take easily take advantage of large, multi-node clusters to solve computational problems.

Current Hadoop deployments exist in the thousands of nodes at companies such as Cloudera, Facebook, Yahoo, etc. However, especially in larger networks, file access latency can be a significant. The Hadoop File System currently does not use local (i.e. on the client) random access memory (RAM) to improve latency.

@@

In this paper, we discuss \textit{Panthera}, a cache layer for Hadoop. In Section 2, we discuss the specific challenges associated with such a project. Section 3 details the architecture differences between a standard Hadoop installation and one with \textit{Panthera}.

@@

There are several systems built on Hadoop that are in widespread use \cite{hbase, cloudbatch, pig}. The Hadoop project is also supported by large corporations with a 
consistent release cycle. Thus, for \textit{Panthera} to be practical, it must operate independently of the existing Hadoop codebase, i.e. as a layer, rather than a modification. This implies that \textit{Panthera} is implemented completely independently of the Hadoop codebase.

>>>>

\documentclass[12pt]{article}

@@

\section{Introduction}
Distributed computing systems are currently employed across academia and industry, with applications varying from market research for department stores to bioinformatics. In particular, the Hadoop distributed system \cite{hadoop} has seen tremendous growth. Hadoop is an open source version of the revolutionary MapReduce system developed at Google. With it, developers can easily take advantage of large, multi-node clusters to solve computational problems.

Current Hadoop deployments exist in the thousands of nodes at companies such as Cloudera, Facebook, Yahoo, etc. However, especially in larger networks, file access latency can be a significant issue. The Hadoop File System currently does not use local (i.e. on the client) random access memory (RAM) to improve latency.

@@

In this paper, we discuss \textit{Panthera}, a cache layer for Hadoop. In Section 2, we discuss the specific challenges associated with such a project. Section 3 details the architecture differences between a standard Hadoop installation and one with \textit{Panthera}.  Sections 4 and 5 detail the differences between metadata and data caching within \textit{Panthera}. Results and conclusions are covered in Sections 6, 7, 8, 9, concluding with a roadmap for future development in Section 10.

@@

There are several systems built on Hadoop that are in widespread use \cite{hbase, cloudbatch, pig}. The Hadoop project is also supported by large corporations with a 
consistent release cycle. Thus, for \textit{Panthera} to be practical, it must operate independently of the existing Hadoop codebase, i.e. as a layer, rather than a modification. This implies that \textit{Panthera} must implemented without a single change in the existing Hadoop codebase, i.e. as a "drop-in" solution.
